Download data

### 2024-02-16 scripts/subsetDataforCrews.Rmd
working towards writing out projects geodata

@@

spp_needed <- read.csv('../data/raw/2024sos_species.csv') %>% 
  filter(contract == 'SNDO') %>% 
  unite('binomial', genus:species) %>% 
  select(binomial, contract)

@@

blm_surf <- st_read(paste0(p, 'Public_land_ownership/BLM_West_simplified/BLM_West_simplified.shp'), quiet = TRUE)
invasives <- rast(paste0(p, 'MRLC/', '2023_InvGrassCover.tif'))
change_intensity <- rast(paste0(p, 'MRLC/total_change_intensity_index/', 'TCII_3arc.tif'))
fire_perimeters <- st_read(
  paste0(p, 'NIFC_perimeters/', 'InterAgencyFirePerimeterHistory_All_Years_View-Simplified.shp'))

@@

#' @param crew_id column in project_areas holding the crews identifier info 'e.g. UFO'
#' @param blm_surf sf data set of surface management as multipolygon at most
#' @param fs_surf sf data set of surface USFS land management as multipolygon at most
#' @param fire sf data set of historic fires as multipopylgon at most
#' @param invasive sf dataset of invasive species relative cover estimates
#' @param historic_SOS sf dataset with historic SoS endeavors and relevant info
#' @param roads sf dataset of roads with relevant attritbutes
#' @param seed_transfer sf dataset of seed transfer zones 
#' @param drought6 netcdf of drought dataset from SPEI website, we recommend using 6 and 12 month
#' @param drought12 12 netcdf of drought dataset from SPEI website, we recommend using 6 and 12 month

>>>>

```{r jitter the AIM data, eval = F}
set.seed(125)
occ_p <- '/media/steppe/hdd/SDM_restorations/data/raw/occurrence/combined_records'
occurrences <- lapply(
  file.path(occ_p, list.files(occ_p, pattern = 'shp$')), st_read, quiet = T) |>
  bind_rows() %>% 
  filter(Occurrence == 1) %>% 
  select(taxon, date, PtType)
occ_aim <- filter(occurrences, PtType == 'AIM Presence') %>% 
  st_jitter(amount = 250)
occurrences <- bind_rows(
  filter(occurrences, PtType != 'AIM Presence'), 
  occ_aim) %>% 
  mutate(
    PtType = if_else(PtType == 'AIM Presence', 'jittered', 'exact'),
    date = str_extract(date, '[0-9]{4}')
    ) %>% 
  rename(year = date, coord_status = PtType) %>% 
  arrange(taxon, year, coord_status)

st_write(occurrences, file.path(occ_p, 'jittered_occurrences.shp'), quiet = T)

rm(occ_p. occ_aim)
```

@@

spp_needed <- read.csv('../data/raw/2024sos_species.csv') %>% 
  filter(contract %in% c('SNDO', 'EASTERN MOJAVE')) %>% 
  unite('binomial', genus:species) %>% 
  select(binomial, contract)

@@

blm_surf <- st_read(paste0(p, 'Public_land_ownership/BLM_West_simplified/BLM_West_simplified.shp'), quiet = TRUE)
usfs_surf <- st_read(paste0(p, 'Public_land_ownership/USFS_West_simplified/USFS_West_simplified.shp'), quiet = TRUE)
invasives <- rast(paste0(p, 'MRLC/', '2023_InvGrassCover.tif'))
change_intensity <- rast(paste0(p, 'MRLC/total_change_intensity_index/', 'TCII_3arc.tif'))
fire_perimeters <- st_read( quiet = T,
  paste0(p, 'NIFC_perimeters/', 'InterAgencyFirePerimeterHistory_All_Years_View-Simplified.shp'))
SWSTZ <- st_read( quiet = T,
  paste0(p, 'provisional_SeedTransferZones/', 'desertSW/desert_southwest_provisional_seed_transfer_zones_USGS.shp')) %>% 
  select(seed_zone = Zone) %>% 
  mutate(Dataset = 'SWSTZ', .before = geometry, seed_zone = as.character(seed_zone))
BOWERSTZ <- st_read( quiet = T,
  paste0(p, 'provisional_SeedTransferZones/', 'WWETAC_STZ/GB_2013_revised_reduced.shp')) %>% 
  select(seed_zone) %>% 
  mutate(Dataset = 'BowerRevised', .before = geometry)
STZ <- bind_rows(BOWERSTZ, SWSTZ)
roads <- st_read(quiet = T, paste0(p, 'blmRoadsSOS24/processed/BLM_roads.shp'))
admin_boundaries <- st_read(paste0(p, 'Public_land_ownership/BLM_ADMU/BLM_ADMU_BOUNDARIES.shp'), quiet = TRUE)
allotments <- st_read(
  file.path(p, 'Public_land_ownership/BLM_Natl_Grazing_Allotment_Polygons/Allotment-simp.shp'))

occ_p <- '/media/steppe/hdd/SDM_restorations/data/raw/occurrence/combined_records'
occurrences <- st_read(file.path(occ_p, 'jittered_occurrences.shp'), quiet = T)

rm(SWSTZ, BOWERSTZ, occ_p)
```

teams_list <- filter(teams, str_detect(Contract, 'SNDO|Eastern Mojave')) %>% 
  split(., f = .$Contract)

lapply(teams_list, project_maker,
       target_species = spp_needed,
       blm_surf = blm_surf,
       fs_surf = usfs_surf, 
       fire = fire_perimeters,
       invasive = invasives,
       total_change = change_intensity,
      # sdm_stack, 
       occurrences = occurrences,
      # historic_SOS, 
       roads = roads, seed_transfer = STZ)

@@
